Exploring the Validity Range of PLL Analytical Models

### 2025-05-15 CaseStudies/Example3_2_LimitsoftheTheorySoFar/Report/article/article.qmd
Finishing the conference of the complete transfer function (l. 335).

# Parâmetros do PLL
C1 = (Kphase * KVCO) / (N * omega_n**2)
C2 = C1 / 10
R1 = (zeta * 4 * np.pi * N * omega_n) / (I * KVCO)
```

@@

An integer-N Phase-Locked Loop (PLL) was developed with a division factor of $N=$ `{python} N`. The system was designed with a VCO gain of $K_\mathrm{VCO}=$ `{python} format(KVCO)`Hz/V, and a charge pump current of $I=$ `{python} format(I)`A. The phase detector gain is given by $K_\theta=\frac{I}{2\pi}$, resulting in $K_\theta=$ `{python} format(Kphase)`A/rad.

@@

>>>>

# Parâmetros do PLL
C1 = (Kphase * KVCO) / (N * omega_n**2)
C2 = C1 / 10
R1 = (zeta * 4 * np.pi * N * omega_n) / (I * KVCO)
Cs = C1 * C2 / (C1 + C2)
```

@@

Using the parameters $\omega_n$ and $\zeta$, the transfer function of the entire loop can be described as (neglecting the second capacitor, $C_2$, of the filter):

$$
\frac{\theta_o}{\theta_R}=\frac{\omega_n^2\left(\frac{2\zeta}{\omega_n}s+1\right)}{s^2+2\zeta\omega_n s+\omega_n^2}
$$ {#eq-full-transfer-function-no-C2}

An integer-N Phase-Locked Loop (PLL) was developed with a division factor of $N=$ `{python} N`. The system was designed with a VCO gain of $K_\mathrm{VCO}=$ `{python} format(KVCO)`Hz/V, and a charge pump current of $I=$ `{python} format(I)`A. The phase detector gain is given by $K_\theta=I/2\pi$, resulting in $K_\theta=$ `{python} format(Kphase)`A/rad.

@@

Similarlly what was presented in [Eq. @eq-full-transfer-function-no-C2], it's possible to present the transfer function of the system in terms of components values. This transfer function can be seen below (this equation uses the second capacitor, $C_2$, of the loop filter, adding a high-frequency pole to the system):

$$
\begin{split}
\frac{\theta_o}{\theta_R}&=\frac{K_\mathrm{VCO}K_\theta\left(1+sC_1R\right)}{s^2N\left(C_1+C_2\right)\left(1+sC_sR\right)+K_\mathrm{VCO}K_\theta\left(1+sC_1R\right)}
\end{split}
$$
